---
output: pdf_document
---
```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=F, warning=FALSE, message=T)
pathtocsv <- "taggeddataset.csv"
suppressMessages(source('vistagdata.R'))
```

# Visualization of tagged data

The report contains the following visualizations.

1. Visualizing objects versus tags
2. Visualizing tags versus objects
3. Hierarchical object clustering (a dendogram)
4. Hierarchical tag clustering (a dendogram)
5. Heatmap of objectwise hierarchical clustering
6. Heatmap of tagwise hierarchical clustering
7. Clusters among objects (using kmeans)
8. Clusters among tags (using kmeans)
9. Number of tags shared by objects
10. Number of objects shared by tags

----

The objects are:
```{r}
objects <- levels(longdat(pathtocsv)[,1])
objects
```

The tags are:
```{r}
tags <- levels(longdat(pathtocsv)[,2])
tags <- subset(tags,tags!="")
tags
```

\newpage

## Visualizing objects versus tags

----

```{r}
qplot(object,fill=tag,data=longdat(pathtocsv),xlab="",ylab="")
```

\newpage

## Visualizing tags versus objects

----

```{r}
qplot(tag,fill=object,data=longdat(pathtocsv,toclassify="tag"),xlab="",ylab="")
```

\newpage

## Hierarchical object clustering

----


```{r}
pathtocsv %>% hcluster
```

\newpage

## Hierarchical tag clustering

----


```{r}
pathtocsv %>% hcluster(toclassify="tag")
```

\newpage

## Heatmap of objectwise hierarchial clustering

----

```{r}
pathtocsv %>% incdat %>% as.matrix %>% heatmap
```

\newpage

## Heatmap of tagwise hierarchial clustering

----

```{r}
pathtocsv %>% incdat(toclassify="tag") %>% as.matrix %>% heatmap
```

\newpage

## Clusters among objects (using kmeans)

----

```{r}
ko <- kmcluster(pathtocsv)
mydat <- data.frame(names=names(sort(ko$cluster)),clustnums=sort(ko$cluster))
rownames(mydat) <- NULL

ggplot()+ geom_bar(data=mydat, aes(x=factor(names,levels=names),y=1), stat="identity",fill=factor(mydat$clustnums))+ coord_flip()+ geom_text(data=mydat, aes(x=factor(names,levels=names), y=1, label=names),color="white",hjust=1)+ labs(x="",y="")+ theme_bw()+ theme(axis.ticks = element_blank(), axis.text.x = element_blank(),axis.text.y = element_blank())

message("The clusters are:")
print(split(names(ko$cluster),ko$cluster))
```

\newpage

## Clusters among tags (using kmeans)

----

```{r}
ko <- pathtocsv %>% kmcluster(toclassify="tag")
mydat <- data.frame(names=names(sort(ko$cluster)),clustnums=sort(ko$cluster))
rownames(mydat) <- NULL

ggplot()+ geom_bar(data=mydat, aes(x=factor(names,levels=names),y=1), stat="identity",fill=factor(mydat$clustnums))+ coord_flip()+ geom_text(data=mydat, aes(x=factor(names,levels=names), y=1, label=names),color="white",hjust=1)+ labs(x="",y="")+ theme_bw()+ theme(axis.ticks = element_blank(), axis.text.x = element_blank(),axis.text.y = element_blank())

message("The clusters are:")
print(split(names(ko$cluster),ko$cluster))
```

\newpage

## Number of tags shared by objects

----

```{r}
pathtocsv %>% sharedtable %>% heatmap
pathtocsv %>% sharedtable %>% print
```

\newpage

## Number of objects shared by tags

----

```{r}
pathtocsv %>% sharedtable(toclassify="tag") %>% heatmap
pathtocsv %>% sharedtable(toclassify="tag") %>% print
```

----

The document with visualizations was generated using the code from the project **Analyzing tagged data** (https://github.com/talegari/analyzing-tagged-data)

----