---
output: html_document
---
```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=T, warning=FALSE, message=T)
```

# Visualization of tagged data

The report contains the following visualizations.

1. Visualizing objects versus tags
2. Visualizing tags versus versus
3. Hierarchical object clustering (a dendogram)
4. Hierarchical tag clustering (a dendogram)
5. Heatmap of objectwise hierarchial clustering
6. Heatmap of tagwise hierarchial clustering
7. Clusters among objects (using kmeans)
8. Clusters among tags (using kmeans)
9. Number of tags shared by objects
10. Number of objects shared by tags

----

The objects are:
```{r}
source('~/vis_tag_data/vistagdata.R')
a <- read.csv("~/vis_tag_data/taggeddataset.csv",fill=T,colClasses="character")
objects <- levels(longdat(a)[,1])
objects
```

The tags are:
```{r}
source('~/vis_tag_data/vistagdata.R')
a <- read.csv("~/vis_tag_data/taggeddataset.csv",fill=T,colClasses="character")
tags <- levels(longdat(a)[,2])
tags <- subset(tags,tags!="")
tags
```

\newpage

## Visualizing objects versus tags

----

```{r}
suppressMessages(require(ggplot2))
source('~/vis_tag_data/vistagdata.R')
a <- read.csv("~/vis_tag_data/taggeddataset.csv",fill=T,colClasses="character")
qplot(object,fill=tag,data=longdat(a),xlab="",ylab="")
```

\newpage

## Visualizing tags versus objects

----

```{r}
suppressMessages(require(ggplot2))
source('~/vis_tag_data/vistagdata.R')
a <- read.csv("~/vis_tag_data/taggeddataset.csv",fill=T,colClasses="character")
qplot(tag,fill=object,data=longdat(a,toclassify="tag"),xlab="",ylab="")
```

\newpage

## Hierarchical object clustering

----


```{r}
suppressMessages(require(dplyr))
source('~/vis_tag_data/vistagdata.R')
a <- read.csv("~/vis_tag_data/taggeddataset.csv",fill=T,colClasses="character")
a %>% longdat %>% incdat %>% hcluster
```

\newpage

## Hierarchical tag clustering

----


```{r}
suppressMessages(require(dplyr))
source('~/vis_tag_data/vistagdata.R')
a <- read.csv("~/vis_tag_data/taggeddataset.csv",fill=T,colClasses="character")
hcluster(incdat(longdat(a),toclassify="tag"))
```

\newpage

## Heatmap of objectwise hierarchial clustering

----


```{r}
suppressMessages(require(dplyr))
source('~/vis_tag_data/vistagdata.R')
a <- read.csv("~/vis_tag_data/taggeddataset.csv",fill=T,colClasses="character")
a %>% longdat %>% incdat %>% hclusterhm
```

\newpage

## Heatmap of tagwise hierarchial clustering

----


```{r}
suppressMessages(require(dplyr))
source('~/vis_tag_data/vistagdata.R')
a <- read.csv("~/vis_tag_data/taggeddataset.csv",fill=T,colClasses="character")
hclusterhm(incdat(longdat(a),toclassify="tag"))
```

\newpage

## Clusters among objects (using kmeans)

----

```{r}
suppressMessages(require(ggplot2))
source('~/vis_tag_data/vistagdata.R')
a <- read.csv("~/vis_tag_data/taggeddataset.csv",fill=T,colClasses="character")
ko <- kmcluster(incdat(longdat(a)))
qplot(names(ko$cluster),fill=ko$cluster,xlab="",ylab="")

message("The clusters are:")
print(split(names(ko$cluster),ko$cluster))
```

\newpage

## Clusters among tags (using kmeans)

----

```{r}
suppressMessages(require(ggplot2))
source('~/vis_tag_data/vistagdata.R')
a <- read.csv("~/vis_tag_data/taggeddataset.csv",fill=T,colClasses="character")
ko <- kmcluster(incdat(longdat(a),toclassify="tag"))
qplot(names(ko$cluster),fill=ko$cluster,xlab="",ylab="")

message("The clusters are:")
print(split(names(ko$cluster),ko$cluster))
```

\newpage

## Number of tags shared by objects

----

```{r}
heatmap(sharedtable(incdat(longdat(a))))
print(sharedtable(incdat(longdat(a))))
```

\newpage

## Number of objects shared by tags

----

```{r}
heatmap(sharedtable(incdat(longdat(a),toclassify="tag")))
print(sharedtable(incdat(longdat(a),toclassify="tag")))
```
